---
title: "Intro: Working with tibbles"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Intro: Working with tibbles}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>"
)
```

```{r setup}
library(opioidLit)
```

## Introduction

Data requests to the OIDA API are returned as tibbles.  Tibbles are special data structures that allow for lists to be nested within the column of a data frame. The `tibble` package is required to create and work with tibbles.

```{r tibble-install, eval=T}
#install.packages("tibble")
library(tibble)
vignette(package = "tibble")
```

## Rectangling tibbles

Extracting list elements from a tibble column is informally known as "rectangling." The process requires patience and vignettes are available for assistance.

```{r rectangle, eval=F}
#install.packages("tidyr")
#install.packages("dplyr")
#install.packages("repurrrsive")
#load packages
library(tidyr)
library(dplyr)
library(repurrrsive)
#load vignette in help window
vignette("rectangle", package = "tidyr")
```

## Flattening tibbles

A user may choose to work with the tibble or flatten the file to a tabular form like the more traditional and ubiquitous data frame. There are at least two choices: (1) `purrr::flatten` or (2) `jsonlite::flatten`.

```{r purrr-flatten, eval=F}
#install.packages("purrr")
library(purrr)
help("flatten", package = "purrr")
```

```{r jsonlite-flatten}
#install.packages("jsonlite")
library(jsonlite)
help("flatten", package = "jsonlite")
```


## Reference

Hadley Wickham and Garret Grolemund (2017). [R for Data Science-Tibbles](https://r4ds.had.co.nz/tibbles.html), O'Reilly Media.
